Human Factors Influencing Visual Statistical Inference

### 2013-06-08 sociology_paper.tex
model fitting description added

\subsection{Learning Trend} Model \eqref{eqn:trend_time} is fitted to the data from experiment 5, 6, and 7. The results are shown in Table \ref{tbl:model_result_time}.  The model is fitted using R function $lmer()$ from package $lme4$. To obtain the $p$-values of fixed effect parameters, normal approximation is used $Z$ scores are computed accordingly.

>>>>

\subsection{Learning Trend} Model \eqref{eqn:trend_time} is fitted to the data from experiment 5, 6, and 7 separately.   For this the function $lmer()$ is used from R package $lme4$ by \cite{lme4:2011}. To obtain the $p$-values of fixed effect parameters estimates, normal approximation is used for $Z$ scores computed as the ratio of estimates to the estimated standard errors. The results are shown in Table \ref{tbl:model_result_time}. Both fixed effect parameters of covariate Attempt ($\alpha_1$ and $\alpha$) are highly significant.
